A seamless, client-centric programming model for type safe web applications

### 2014-05-07 paper.tex
Further emphasize that it's a library.

Our model is client-centric, in that the client drives the application while
the server takes on the role of passively serving client requests, and is based
on a simple blocking concurrency model rather than explicit continuations.
It is well suited for use with a GUI programming style based on
self-contained processes with local state, and requires essentially no
modification of existing tools or compilers.

>>>>

Our model is client-centric, in that the client drives the application while
the server takes on the role of passively serving client requests, and is based
on a simple blocking concurrency model rather than explicit continuations.
It is well suited for use with a GUI programming style based on
self-contained processes with local state, and requires no modification of
existing tools or compilers, being implemented completely as a library.
